### 2022-01-07 src-latex/parts/50-xp-setup.tex

\subsection{Training procedure}
5-fold CV for all models.
\begin{itemize}
\item Spacy CNN : no limits on the number of epochs, instead use patience=1600.
\item CamemBERT : 3 epochs.
\end{itemize}

>>>>

\subsection{Training procedure}
\begin{itemize}
\item Spacy CNN : do not put a limit on epochs, instead use patience=1600.
\item CamemBERT : 3 epochs.
\end{itemize}

Split the full dataset into 80 percent train, 10 percent dev / eval and 10 percent test.
Use stratified sampling based on the directory name. This way each set contains samples of all directories.
